### 2024-04-09 Introduction+SummaryStats.Rmd
new data set added, NAs are not removed (need to replace with averages)

```{r}
TempData <- read_excel("Temperature2011-2021 (1).xlsx")
TempData <- TempData |>
  mutate(
    `Decimal Years` = date(date_decimal(`Decimal Years`))) |>
  na.omit()

  colnames(TempData) <- c("Date", "Temp", "SD")
```

>>>>

```{r}
TempData <- read_excel("~/WaterTemperature_TSA_FinalProject/picodataexport-temperatureNew.xlsx", col_names = FALSE,     col_types = c("numeric", "numeric", "numeric"))

colnames(TempData) <- c("Date", "Temp", "SD")

TempData <- TempData |>
  mutate(
    Date = date(date_decimal(Date)))

```
